---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# drake_test01

A demo of using [Drake](https://github.com/ropensci/drake) for more reproducible research.

R directory contains:

1. packages.R to load packages needed
2. plan.R to generate a Drake plan
3. other scripts to create functions used in plan

In the root dirctory make.R will 'source' all the R scripts and run the plan.

To try use: ```source("make.R")```

```{r, include = FALSE}
source("make.R")
```


Look at the plan with:

```{r}
ians_analysis
```

Load in the objects that Drake makes with, for example: ```loadd(cars_summary)```

Then it'll be in your R workspace...

```{r, include = FALSE}
source("make.R")
loadd(cars_summary)
```



```{r}
ls()

cars_summary
```


Or read it directly e.g.

```{r}
print(readd(cars_summary))
```

If you change the plan and then run make.R only the targets that depend on the changes will be re-run!



